A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Add blurb about why all of a sudden there's a bunch of Haste stuff.
Reference Cloud Haskell in implementation section.

@@

The second argument of the \lstinline!Export! constructor is, as the observant
reader might have guessed, the list of arguments to be sent to the export,
to be updated as the exported function is applied using the \lstinline!<.>!
operator.

@@

@@

\paragraph{Inspiration and alternatives to \lstinline!export!} One crucial
aspect of implementing cross-network function calls is the issue of data
representation: the client side of things must be able to obtain some
representation of any function it may want to call on the server.

>>>>

This concept of client-side identifiers being sent to the server and used as
indices into a table mapping identifiers to remotely accessible functions is an
extension of the concept of ``static values'' introduced by Epstein et al with
Cloud Haskell\ \cite{cloudhaskell}, which is discussed further in section
\ref{sec:cloudhaskell}.

@@

The second argument of the \lstinline!Export! constructor is the list of
arguments to be sent to the export, to be updated as the exported function is
applied using the \lstinline!<.>! operator.

@@

As Haste has not been published elsewhere, we describe here some key elements
of its design and implementation which are pertinent to this work.

@@

\paragraph{Inspiration and alternatives to \lstinline!export!}
\label{sec:cloudhaskell}
One crucial aspect of implementing cross-network function calls is the issue of
data representation: the client side of things must be able to obtain some
representation of any function it may want to call on the server.
